%%fakesection Preamble
\usepackage{ccicons}
\usepackage{booktabs}

\newcommand{\shorturl}[2]%
  [?utm\_source=jsc\&utm\_medium=presentation\&utm\_campaign=jiscmrd\_workshop\_oct\_2012]%
  {\href{http://#2#1}{\nolinkurl{#2}}}

\usetheme{Bath}

\setbeamercovered{transparent}
\setbeamertemplate{blocks}[rounded]
\setbeamercolor{block title}{bg=Research,fg=white}
\setbeamercolor{block body}{bg=Research!30!white}


\title{RDM training for students and staff}
\subtitle{Progress and observations}
\author[Jez Cope]{Jez Cope\\ Technical Data Co-ordinator}
\institute[Bath]{Centre for Sustainable Chemical Technologies\\ University of Bath}
\date[25 October 2012]{JISC MRD/DCC Progress Workshop\\ \textit{Thursday 25 October 2012}}

%\AtBeginSection[]
%{
%  \begin{frame}<beamer>
%    \tableofcontents[sectionstyle=show/shaded,subsectionstyle=show/show/shaded]
%  \end{frame}
%}

%-----------------------------------------------------------------------------
\begin{document}
%%fakesection Front matter
%-----------------------------------------------------------------------------

\begin{frame}[plain]
  \titlepage
\end{frame}

\begin{frame}
  \tableofcontents
\end{frame}

\section{Introduction}

\begin{frame}
  \frametitle{Aims and objectives: for us}
  
  \begin{itemize}[<+>]
    \item Raise awareness of the issues;
    \item Engage students with policy \& infrastructure development;
    \item Reduce risks, e.g.
      \begin{itemize}[<.>]
        \item Data loss;
        \item Unauthorised access;
      \end{itemize}
    \item Promote support services.
  \end{itemize}

\end{frame}

\begin{frame}
  \frametitle{Aims and objectives: for learners}
  
  \begin{itemize}[<+>]
    \item ``Storing data on a computer in a way that's easy to go back to''
    \item ``Keeping track of papers/info''
    \item ``Tracking phases of data''
    \item ``Storing data efficiently''
    \item ``Tracking data from multiple experiments''
    \item ``Software to manage data''
  \end{itemize}

\end{frame}

%\begin{frame}
%  \frametitle{Pre-research360}
  
  
%\end{frame}

\section{What we did}

\begin{frame}
  \frametitle{What we did}
  
  \begin{block}{Hands on DMP workshop}
    \begin{itemize}
      \item Presentation from senior academic;
      \item Discussions encouraged;
      \item Dedicated time to create a DMP.
    \end{itemize}
  \end{block}
\end{frame}

\begin{frame}
  \frametitle{What we did}
  
  \begin{block}{Lecture-style workshop}
    Some interactivity:
    \begin{itemize}
      \item Clickers to gather overall opinions;
      \item Brief discussions about definitions;
      \item Primarily didactic.
    \end{itemize}
  \end{block}
\end{frame}

\begin{frame}
  \frametitle{What we did}
  
  \begin{block}{Interactive workshop}
    Highly interactive:
    \begin{itemize}
      \item Majority of time spent on discussions;
      \item Discussion guided by specific questions/tasks;
      \item Plenary sections to highlight good/bad practice.
    \end{itemize}
  \end{block}
\end{frame}
\section{General observations}

\begin{frame}
  \frametitle{What worked well}
  
  \setbeamertemplate{itemize items}{\checkmark}
  \begin{itemize}[<+>]
    \item Postgraduate-specific DMP template;
    \item Dedicated time to do planning;
    \item Clickers to determine current knowledge/perceptions;
    \item Discussion within group to share good practice.
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{What didn't work so well}
  
  \setbeamertemplate{itemize items}{?}
  \begin{itemize}[<+>]
    \item Not addressing the ``Dropbox issue'';
    \item Not recommending specific software/processes;
    \item Too much discussion.
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{General observations}
  
  \begin{itemize}[<+>]
    \item Learners just want to be told what to do;
    \item Attendance has been excellent;
    \item Good practices are there, but patchy.
  \end{itemize}
\end{frame}

\section{Questions}

\begin{frame}
  \frametitle{Questions}
  
  \begin{itemize}
    \item What's the best balance between lecturing, discussion and hands-on?
    \item How do we bring in more research staff?
    \item What are the training needs of support/professional staff?
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Further support}
  
  \begin{itemize}
    \item Subject specific examples, processes, resources;
    \item Train the trainer;
    \item OER slides and activities to draw on.
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{More information}

  \begin{center}
    \small
    \begin{tabular}{rl}
      \toprule
      Research360 blog    & \shorturl{blogs.bath.ac.uk/research360} \\
      Bath RDM web pages  & \shorturl{bath.ac.uk/research/data/} \\
      PGR DMP template    & \shorturl{opus.bath.ac.uk/30772/} \\
      Lecture slides      & \shorturl{bit.ly/rdm-101-lecture-slides} \\
      Workshop slides     & \shorturl{bit.ly/rdm-101-workshop-slides} \\
      \bottomrule
    \end{tabular}
    
    \bigskip
    \href{http://creativecommons.org/licenses/by-sa/3.0/}{\ccbysa}
  \end{center}
\end{frame}

\end{document}
